\documentclass[line,margin]{res} 
\usepackage{comment}

\begin{document}

\name{Jane A. Sandberg}
% \address used twice to have two lines of address
\address{6500 Pacific Blvd SW -- Albany, Oregon, 97321}
\address{\hspace{.3in} sandbej@linnbenton.edu -- (541) 917 4655}
\renewcommand{\labelitemi}{$\ddagger$}

\begin{resume}
 
     \section{EDUCATION}
  {\sl Master of Library and Information Science}\hfill August 2011 - May 2013\\
    University of Illinois, Urbana, Illinois \\
    Certificate in Community Informatics \\
    
%    {\sl Non-degree Coursework in Computer Science} \hfill August 2012 - May 2013\\
%    Parkland College, Champaign, Illinois

    {\sl Bachelor of Music} \hfill August 2006 - December 2010\\
    Oberlin College, Oberlin, Ohio \\

\vspace{12pt}

 
\section{LIBRARY \\ EXPERIENCE}
  {\sl Electronic Resources Librarian} \hfill September 2014 - present \\
  Linn-Benton Community College, Albany, Oregon
    \begin{itemize}  \itemsep -1pt % reduce space between items
      \item Implemented a Blacklight-based discovery layer
      \item Chaired a committee focusing on campus OER adoption
      \item Organized professional development opportunities for catalogers in our consortium
      \item Evaluated consortial shared catalog and led projects to improve its quality
      \item Acted as ILS administrator and primary contact for database vendors
      \item Performed original cataloging
      \item Provided information literacy sessions for classes in various disciplines
    \end{itemize}
\vspace{8pt}

{\sl Adult Services Librarian} \hfill May 2013 - September 2014 \\
  Burlington Public Library, Burlington, Washington
    \begin{itemize}  \itemsep -1pt % reduce space between items
      \item Led the automation of the library's acquisitions process
      \item Served as primary contact person for library materials vendors
      \item Oversaw several reclassification projects
      \item Selected music and world language materials for the library's collection
      \item Planned and implemented diverse programs for adults
      \item Co-designed an engaging weekly workshop for English Language learners
      \item Supervised library volunteers
    \end{itemize}
\vspace{8pt}
    {\sl Slavic Cataloging Graduate Assistant} \hfill August 2011 - May 2013 \\
  University of Illinois, Urbana, Illinois
    \begin{itemize}  \itemsep -1pt % reduce space between items
      \item Provided original and derived catalog records for books and microforms in several Slavic and East European languages
      \item Developed macros for cataloging staff to facilitate the implementation of the emerging Resource Description and Access (RDA) cataloging code
      \item Co-facilitated RDA training sessions for catalogers
      \item Maintained online documentation to support the library's transition to RDA
    \end{itemize}

\vspace{8pt}
 
  {\sl Junior Fellow Summer Intern} \hfill June - August 2009 \\
  Library of Congress, Washington, District of Columbia
    \begin{itemize}  \itemsep -1pt
      \item Created original records for books and musical scores
      \item Assigned call numbers using Library of Congress Classification
    \end{itemize}
\vspace{8pt}

    \newpage
\section{BOOK \\ CHAPTERS}
      Sandberg, J. A. (2015). Toward a new digital practice: organizing the transgender Internet. In R. Wexelbaum, \emph{Queers online: LGBT digital practices in libraries, archives, and museums} (pp. 44-60). Duluth, Minn.: Library Juice Press.

\section{REFEREED \\ JOURNAL \\ ARTICLES}
      Jin, Q. \& Sandberg, J. A. (2014). Implementing RDA at the University of Illinois at Urbana-Champaign Library.  \emph{Technical Services Quarterly, 31}(3).

\section{REVIEWS}
      Sandberg, J. A. (2015). Beyond magenta: transgender teens speak out.  \emph{GLBT Reviews}.

      Sandberg, J. A. (2015). BIBFRAME Editor. \emph{Technical Services Quarterly, 32}(2).

      Sandberg, J. A. (2015). Structured Data Linter.  \emph{Technical Services Quarterly, 32}(3).

      Sandberg, J. A. (2015). Transgender lives: complex stories, complex voices.  \emph{GLBT Reviews}.

      Sandberg, J. A. (2014). Better living through macros.  \emph{Technical Services Quarterly, 31}(2).

      Sandberg, J. A. (2014). End of the rainbow.  \emph{GLBT Reviews}.

      Sandberg, J. A. (2014). Red caps: new fairy tales for out of the ordinary readers.  \emph{GLBT Reviews}.



\section{COURSES \\ TAUGHT}
Destination Graduation, HD120

Computer Basics for Non-native English Speakers, ESOL 0.792E

\vspace{12pt}
\section{RESEARCH \\ INTERESTS}
\begin{itemize}
\item Library linked data and authority control
\item Evidence-based evaluation of cataloging practices
\item Information needs of transgender people
\item Information-seeking behavior of community college students
\item Intersections between librarianship and social work
\item Open Source Library Software
\end{itemize}

\vspace{12pt}


\section{PROFESSIONAL \\ MEMBERSHIPS}
\begin{itemize}
 \item Member, American Library Association
 \item Member, ALA GLBT Round Table
 \item Member, ALA GLBT Round Table Resources Committee
 \item Member, REFORMA: the national association to promote library and information services to Latinos and the Spanish-speaking
\end{itemize}

\vspace{12pt}

\section{CONFERENCE \\ PRESENTATIONS}
\begin{itemize}
 \item \emph{Transgender Internet curators 1994-2010: their values and impact}. (2016, March). Poster session presented at the Moving Trans History Forward conference, Victoria, BC.
\end{itemize}

\end{resume}
\end{document}
